\documentclass[../DoAn.tex]{subfiles}
\begin{document}

\begin{center}
    \Large{\textbf{ABSTRACT}}\\
\end{center}
\vspace{1cm}
In the context of robust development in information technology, the demand for online communication via messaging and video calls is rapidly increasing. This necessitates applications that ensure high speed, low latency, and effective multimedia processing. While existing solutions are widespread, self-building and mastering real-time transmission and video streaming technologies remain significant technical challenges for optimizing user experience under varying network conditions.

To address this problem, this project implements a system based on Client-Server architecture. The system utilizes real-time protocols such as WebSocket and WebRTC to handle messaging and calling tasks, ensuring instant user interaction. A key highlight of the project is the integration of HLS (HTTP Live Streaming) technology for video content processing. HLS segments video content, optimizing transmission and allowing users to experience smooth playback with low latency, adapting effectively to network bandwidth fluctuations.

The solution is realized as a comprehensive web application featuring registration, authentication, friend search, multimedia messaging, and video calling. The application of HLS demonstrates clear effectiveness in improving video transmission and playback within conversations.

The result is a stable messaging and calling system that satisfies requirements for real-time performance and multimedia processing. The project provides an effective reference model for combining real-time services with modern streaming techniques in web application development.

\end{document}